Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-17 ms.tex
added some observing details in a table.

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.

@@

We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).

>>>>

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from \citet{morton2016falsePos} and this work.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis in terms of stellar radii, which can be combined with Kepler's third law to calculate the stellar density \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.
In this section, we analyze available high resolution spectra to put new constraints on the stellar temperature and surface gravity.

@@

We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
The orbital phases during the observations were in the range f
None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).

\begin{deluxetable}{cccccccc}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\end{deluxetable}
